MINOS Transition Models

### 2022-12-16 docsrc/Coefficients/summarise_transitions_2.tex
make html wider so it doesnt wrap
adjust Rmd width to prevent wrapping

\hypertarget{setup}{%
\section{Setup}\label{setup}}

\hypertarget{tobacco}{%
\subsection{Tobacco}\label{tobacco}}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{require}\NormalTok{(tidyverse)}
\end{Highlighting}
\end{Shaded}

@@

\begin{verbatim}
## -- Attaching packages --------------------------------------- tidyverse 1.3.2 --
## v ggplot2 3.3.6      v purrr   0.3.4 
## v tibble  3.1.8      v dplyr   1.0.10
## v tidyr   1.2.0      v stringr 1.4.0 
## v readr   2.1.2      v forcats 0.5.1 
## -- Conflicts ------------------------------------------ tidyverse_conflicts() --
## x dplyr::filter() masks stats::filter()
## x dplyr::lag()    masks stats::lag()
\end{verbatim}

@@

\begin{verbatim}
## 
## Call:
## zeroinfl(formula = y ~ factor(sex) + scale(age) + scale(SF_12) + factor(labour_state) | 
##     relevel(factor(ethnicity), ref = "WBI") + scale(age), data = data, 
##     dist = "pois")
## 
## Pearson residuals:
##      Min       1Q   Median       3Q      Max 
## -1.75024 -0.76329 -0.05563  0.58683 17.88004 
## 
## Count model coefficients (poisson with log link):
##                                      Estimate Std. Error z value Pr(>|z|)    
## (Intercept)                          1.158187   0.024071  48.116  < 2e-16 ***
## factor(sex)Male                      0.106336   0.025077   4.240 2.23e-05 ***
## scale(age)                           0.107561   0.017073   6.300 2.97e-10 ***
## scale(SF_12)                        -0.029366   0.013324  -2.204 0.027518 *  
## factor(labour_state)Family Care      0.207191   0.057175   3.624 0.000290 ***
## factor(labour_state)Maternity Leave -0.302883   0.501065  -0.604 0.545525    
## factor(labour_state)PT Employed      0.039547   0.044232   0.894 0.371273    
## factor(labour_state)Retired         -0.028738   0.042805  -0.671 0.501989    
## factor(labour_state)Self-employed    0.006792   0.047900   0.142 0.887239    
## factor(labour_state)Sick/Disabled    0.107874   0.044940   2.400 0.016377 *  
## factor(labour_state)Student         -0.391335   0.101514  -3.855 0.000116 ***
## factor(labour_state)Unemployed       0.052690   0.047488   1.110 0.267196    
## 
## Zero-inflation model coefficients (binomial with logit link):
##                                             Estimate Std. Error z value
## (Intercept)                                 -1.74690    0.06856 -25.480
## relevel(factor(ethnicity), ref = "WBI")BAN  -0.14975    0.51269  -0.292
## relevel(factor(ethnicity), ref = "WBI")BLA  -0.65053    0.86881  -0.749
## relevel(factor(ethnicity), ref = "WBI")BLC   0.31791    0.40897   0.777
## relevel(factor(ethnicity), ref = "WBI")CHI   1.51817    0.70312   2.159
## relevel(factor(ethnicity), ref = "WBI")IND   0.52296    0.36411   1.436
## relevel(factor(ethnicity), ref = "WBI")MIX   0.20122    0.35581   0.566
## relevel(factor(ethnicity), ref = "WBI")OAS   0.93407    0.60401   1.546
## relevel(factor(ethnicity), ref = "WBI")OBL -13.01639  538.48954  -0.024
## relevel(factor(ethnicity), ref = "WBI")OTH  -0.19411    0.99293  -0.195
## relevel(factor(ethnicity), ref = "WBI")PAK   0.03483    0.37297   0.093
## relevel(factor(ethnicity), ref = "WBI")WHO  -0.17955    0.31947  -0.562
## scale(age)                                  -0.31921    0.06479  -4.927
##                                            Pr(>|z|)    
## (Intercept)                                 < 2e-16 ***
## relevel(factor(ethnicity), ref = "WBI")BAN   0.7702    
## relevel(factor(ethnicity), ref = "WBI")BLA   0.4540    
## relevel(factor(ethnicity), ref = "WBI")BLC   0.4370    
## relevel(factor(ethnicity), ref = "WBI")CHI   0.0308 *  
## relevel(factor(ethnicity), ref = "WBI")IND   0.1509    
## relevel(factor(ethnicity), ref = "WBI")MIX   0.5717    
## relevel(factor(ethnicity), ref = "WBI")OAS   0.1220    
## relevel(factor(ethnicity), ref = "WBI")OBL   0.9807    
## relevel(factor(ethnicity), ref = "WBI")OTH   0.8450    
## relevel(factor(ethnicity), ref = "WBI")PAK   0.9256    
## relevel(factor(ethnicity), ref = "WBI")WHO   0.5741    
## scale(age)                                 8.35e-07 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1 
## 
## Number of iterations in BFGS optimization: 30 
## Log-likelihood: -5657 on 25 Df
\end{verbatim}

>>>>

\hypertarget{tobacco-coefficients}{%
\section{Tobacco Coefficients}\label{tobacco-coefficients}}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{options}\NormalTok{(}\AttributeTok{width=}\DecValTok{120}\NormalTok{)}
\FunctionTok{require}\NormalTok{(tidyverse)}
\end{Highlighting}
\end{Shaded}

@@

\begin{verbatim}
## -- Attaching packages ------------------------------------------------------------------------------- tidyverse 1.3.2 --
## v ggplot2 3.3.6      v purrr   0.3.4 
## v tibble  3.1.8      v dplyr   1.0.10
## v tidyr   1.2.0      v stringr 1.4.0 
## v readr   2.1.2      v forcats 0.5.1 
## -- Conflicts ---------------------------------------------------------------------------------- tidyverse_conflicts() --
## x dplyr::filter() masks stats::filter()
## x dplyr::lag()    masks stats::lag()
\end{verbatim}

@@

\begin{verbatim}
## 
## Call:
## zeroinfl(formula = y ~ factor(sex) + scale(age) + scale(SF_12) + factor(labour_state) | relevel(factor(ethnicity), 
##     ref = "WBI") + scale(age), data = data, dist = "pois")
## 
## Pearson residuals:
##      Min       1Q   Median       3Q      Max 
## -1.75024 -0.76329 -0.05563  0.58683 17.88004 
## 
## Count model coefficients (poisson with log link):
##                                      Estimate Std. Error z value Pr(>|z|)    
## (Intercept)                          1.158187   0.024071  48.116  < 2e-16 ***
## factor(sex)Male                      0.106336   0.025077   4.240 2.23e-05 ***
## scale(age)                           0.107561   0.017073   6.300 2.97e-10 ***
## scale(SF_12)                        -0.029366   0.013324  -2.204 0.027518 *  
## factor(labour_state)Family Care      0.207191   0.057175   3.624 0.000290 ***
## factor(labour_state)Maternity Leave -0.302883   0.501065  -0.604 0.545525    
## factor(labour_state)PT Employed      0.039547   0.044232   0.894 0.371273    
## factor(labour_state)Retired         -0.028738   0.042805  -0.671 0.501989    
## factor(labour_state)Self-employed    0.006792   0.047900   0.142 0.887239    
## factor(labour_state)Sick/Disabled    0.107874   0.044940   2.400 0.016377 *  
## factor(labour_state)Student         -0.391335   0.101514  -3.855 0.000116 ***
## factor(labour_state)Unemployed       0.052690   0.047488   1.110 0.267196    
## 
## Zero-inflation model coefficients (binomial with logit link):
##                                             Estimate Std. Error z value Pr(>|z|)    
## (Intercept)                                 -1.74690    0.06856 -25.480  < 2e-16 ***
## relevel(factor(ethnicity), ref = "WBI")BAN  -0.14975    0.51269  -0.292   0.7702    
## relevel(factor(ethnicity), ref = "WBI")BLA  -0.65053    0.86881  -0.749   0.4540    
## relevel(factor(ethnicity), ref = "WBI")BLC   0.31791    0.40897   0.777   0.4370    
## relevel(factor(ethnicity), ref = "WBI")CHI   1.51817    0.70312   2.159   0.0308 *  
## relevel(factor(ethnicity), ref = "WBI")IND   0.52296    0.36411   1.436   0.1509    
## relevel(factor(ethnicity), ref = "WBI")MIX   0.20122    0.35581   0.566   0.5717    
## relevel(factor(ethnicity), ref = "WBI")OAS   0.93407    0.60401   1.546   0.1220    
## relevel(factor(ethnicity), ref = "WBI")OBL -13.01639  538.48954  -0.024   0.9807    
## relevel(factor(ethnicity), ref = "WBI")OTH  -0.19411    0.99293  -0.195   0.8450    
## relevel(factor(ethnicity), ref = "WBI")PAK   0.03483    0.37297   0.093   0.9256    
## relevel(factor(ethnicity), ref = "WBI")WHO  -0.17955    0.31947  -0.562   0.5741    
## scale(age)                                  -0.31921    0.06479  -4.927 8.35e-07 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1 
## 
## Number of iterations in BFGS optimization: 30 
## Log-likelihood: -5657 on 25 Df
\end{verbatim}
